\begin{center}
    \section*{Acknowledgement}
\end{center}
\large We are deeply thankful to Bangladesh University of Business and Technology (BUBT) for providing us such a wonderful environment to peruse our research. We would like to express our sincere gratitude to supervisor name, Assistant Professo, Department of CSE, BUBT. We have completed our research with his help. We found the research area, topic, and problem with his suggestions. He guided us with our study, and supplied us many research papers and academic resources in this area. He is patient and responsible. When we had questions and needed his help, he would always find time to meet and discuss with us no matter how busy he was.  We would also like to acknowledge our team members for supporting each other and be grateful to our university for providing  this opportunity for us.Online food ordering systems have become an essential part of the restaurant industry, offering customers a convenient and easy way to order food from the comfort of their own homes or offices. These systems allow restaurants to expand their customer base, increase revenue, and streamline their operations. Additionally, online food ordering systems have become even more important during the COVID-19 pandemic, as many customers prefer to order food for delivery or takeout rather than dining in. The use of these systems has helped restaurants to adapt to the changing needs of their customers and maintain their businesses during these challenging times. Overall, online food ordering systems are an important tool for both customers and restaurants, providing a seamless and efficient way to order and deliver food