\begin{center}
    \section*{\fontsize{20}{20}\selectfont Chapter 1}
\end{center}
\vspace{5mm}
\section{Introduction}
The new situation created due to Corona, people are turning to online and home delivery to a greater extent than before. Also, climate change along with the way the environment is getting polluted and even unbearable traffic jams have forced people to turn to online ordering. However, in many restaurants, if customers face obstacles while placing their food orders online, it might create problems in your sales, as well as market reputation. Our proposed system is an online food ordering system that is user-friendly for its users.

 Moreover, the basic problem in the food service industry is not realizing efficiencies that would result from better applications of technology. In the other words, third parties should be removed from the system, and thus direct interaction between consumers and restaurants can be introduced.
 
On the other hand, there are many issues that a customer faces during using a food ordering application, and those issues should be acknowledged. A customer wants various services to be supplied by the restaurant management system for a simple and convenient service.

There are many problems that a customer face and those should get utter attention. A customer demands various facilities to be supplied by the restaurant management system for a smooth and convenient service. The rising internet-based dependability of customers is considered another motivation. This system is to increase efficiency by shortening the purchasing time and eliminating paperwork like receipts through online transactions. Keeping the present food crisis across the world in mind, Reducing restaurant's food wastage is another motivation.

Additionally, the system will take input from the user. Consequently, the major attributes that will give input to the database are -name, address, email address, mobile number, and other individual information, etc. Meanwhile, inhabitants are facing difficulties when they are moving to other places and this project will help solve this problem.

Lastly, this project will be cooperative for both the users and food providers. Eventually, this project will successfully make the whole process more appropriate for the users especially.
\begin{itemize}
 %\begin{itemize}
    \item We are innovating through survey
    \item We used cognitive method for this software
    \item We have prepared the questionnaire
    \item We are conducting subject preparation and a survey
    \item We performed a weighted average of survey questions based on user data
%\end{itemize}
\end{itemize}




%\subsection{Problem Statement}
    

%\subsection{Problem Background}
%Write Problem Background in chapter1.tex

%\subsection{Research Objectives}
%Write Research Objectives in chapter1.tex

 %\begin{itemize}
   % \item 
   % \item 
% \end{itemize}
 
 
%\subsection{Motivations}
%Write Motivations in chapter1.tex

%\subsection{Flow of the Research}
%Write Flow of the Research in chapter1.tex

%\begin{figure}[htbp]
%%\caption{Figure.}
%\label{fig1}
%\end{figure}

%\subsection{Significance of the Research}
%Write Significance of the Research in chapter1.tex

%%%\begin{itemize}

  %  \item 
  %  \item 
%\end{itemize}
 
%\subsection{Thesis Organization}
%Write Thesis Organization in chapter1.tex


%\subsection{Summary}
%Write Summary in chapter1.tex 